A new method to estimate dark matter halo concentrations

### 2015-09-22 paper/article.tex
starting to write the conclusions

>>>>

In this paper, we presented a new method to estimate the
concentration of dark matter halos in N-body simulations. 
We tested our method on mock halo data to study the impact of total
number of particles and input concentration on the retrieved values.
We compared these results against two other methods commonly used in
the literature to estimate concentrations.
Finally, we applied our method to halos extracted from a cosmological
N-body simulation to estimate the impact of our method on the mass
concentration relationship.

Comparison against other methods.\\

The effect of the number of particles.\\

The effect of the input concentration.\\

The impact on the mass-concentration relationship.\\

Comment and future.\\
